Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-12-08 ms.tex
Getting rid chi parameter

When possible our results are expressed in terms of the wind heating
parameter $v_{\rm w,0}$; the power-law slope of the density profile
$n$ (also evaluated at $r = \rs$); and the dimensionless parameter \be
\chi \equiv v_{\rm w}^{2}/v_{\rm w,0}^{2} \approx \left(1 + \sigma^{2}/v_{\rm w,0}^{2}\right) \approx
\left(1+0.14 \Mbheight^{0.43}v_{500}^{-1}\right), \ee where $v_{500}
\equiv v_{w,0}/500$ km s$^{-1}$, $M_{\bullet,8} \equiv
M_{\bullet}/10^{8}M_{\odot}$, and the second equality makes use of the
$M_{\bullet}-\sigma$ correlation (\citealt{Gultekin+09}) \be
M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
      km\,s^{-1}}}\right)^{5.1}M_{\odot}.
\label{eq:Msigma}
\ee
Although the use of equation (\ref{eq:Msigma}) is questionable for low mass BHs (e.g., \citealt{Greene&Ho07}), our results are not particularly sensitive to this assumption.

>>>>

When possible our results are expressed in terms of the wind heating
parameter $\vw$; the power-law slope of the density profile
$n$ (also evaluated at $r = \rs$); Note that $\vw^2=\vw0^2+\sigma^2$,
where the $\sigma$ accounts for shock heating between stellar winds moving
with respect to each other with relative velocity $\sigma$, and $\vwO$
is a free parameter accounting for additional sources of
heating.  $\vw$ may be calculated analytically (for a given $\Mbh$ and
$\vwO$) using $\vw=\chi \vwO$, where

 \begin{align}
&\chi^2 \equiv v_{\rm w}^{2}/v_{\rm w,0}^{2} \approx \left(1 +
  \sigma^{2}/v_{\rm w,0}^{2}\right) \approx \\
&\left(1+0.14 \Mbheight^{0.43}\frac{\vwO}{500 {\rm km/s}}^{-1}\right), 
\end{align}

% where $v_{500} $M_{\bullet,8} \equiv
where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$, and the
second equality makes use of the $M_{\bullet}-\sigma$ correlation
(\citealt{Gultekin+09})

 \begin{align}
M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
      km\,s^{-1}}}\right)^{5.1}M_{\odot}.
\label{eq:Msigma}
\end{align}

Although the use of equation (\ref{eq:Msigma}) is questionable for low mass BHs (e.g., \citealt{Greene&Ho07}), our results are not particularly sensitive to this assumption.
